MPA Gap Analysis: IUCN and AquaMaps

### 2016-02-19 mpa_analysis/mpa_analysis.Rmd
kjhgf

rast_marine_file <- file.path(dir_git, 'mpa_analysis/rast_marine.tif')
reload <- FALSE
if(reload == TRUE) {
### import OHI regions polygons, to determine spatially-marine areas
  poly_marine_file <- file.path(dir_anx, 'explore_am_v_iucn/mpa_rasters/poly_marine.shp')
  if(!file.exists(poly_marine_file)) {
    dir_rgn   <- file.path(dir_N, 'git-annex/globalprep/spatial/v2015/data')
    lyr_rgn <- 'regions_gcs'
    poly_rgn <- readShapePoly(file.path(dir_rgn, lyr_rgn), 
                               proj4string = crs_wgs84)

@@

    poly_mar_union <- raster::union(poly_marine)
    poly_mar_union <- rgeos::gUnaryUnion(poly_marine)

    # writePolyShape(poly_marine, poly_marine_file)
    writeOGR(obj    = poly_mar_union,
             dsn    = path.expand(dirname(poly_marine_file)),
             layer  = str_replace(basename(poly_marine_file), '.shp', ''),
             driver = 'ESRI Shapefile',
             overwrite_layer = TRUE,
             verbose = TRUE)

>>>>

rast_marine_file <- file.path(dir_git, 'mpa_analysis/rast_marine.tif')
reload <- FALSE
if(reload == TRUE) {
### import OHI regions polygons, to determine spatially-marine areas
  poly_marine_file <- file.path(dir_anx, 'explore_am_v_iucn/mpa_rasters/poly_marine1.shp')
  if(!file.exists(poly_marine_file)) {
    dir_rgn   <- file.path(dir_N, 'git-annex/globalprep/spatial/v2015/data')
    lyr_rgn <- 'regions_gcs'
    poly_rgn <- readShapePoly(file.path(dir_rgn, lyr_rgn), 
                               proj4string = crs_wgs84)

@@

    poly_list <- list()
    poly_rows <- nrow(poly_marine)
    n_entities <- 20
    for (i in 1:ceiling(poly_rows/n_entities)) { # i = 1
      min_row <- (i - 1) * n_entities + 1
      max_row <- min(i * n_entities, poly_rows)
      poly_tmp <- poly_marine[min_row:max_row, ]
      message(sprintf('%s. Entities [%s:%s]', i, min_row, max_row))
      print(system.time({
        poly_tmp2 <- rgeos::gUnaryUnion(poly_tmp)
      })[3])
      poly_list[i] <- poly_tmp2
    }

    poly_mar_frankenstein <- spRbind(poly_list)

    # poly_mar_union <- rgeos::gUnaryUnion(poly_marine)

    # writePolyShape(poly_marine, poly_marine_file)
    writeOGR(obj    = poly_mar_frankenstein,
             dsn    = path.expand(dirname(poly_marine_file)),
             layer  = str_replace(basename(poly_marine_file), '.shp', ''),
             driver = 'ESRI Shapefile',
             overwrite_layer = TRUE,
             verbose = TRUE)
